Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-06-26 output/latex/manuscript.tex
crispr: fix figure legend
code availability: update statement based on crispr changes

We used Python 3.8 and R 3.6 with several computational packages.
The main Python packages used were: Jupyter Lab (2.2), pandas (1.1), matplotlib (3.3), seaborn (0.11), numpy (1.19), scipy (1.5), scikit-learn (0.23), and umap-learn (0.4).
The main R packages were: Bioconductor (3.10), clusterProfiler (3.14), clustree (0.4), and fgsea (1.17).
We also developed several scripts and notebooks which are published under an open-source license.
We documented all the steps necessary to carry out all the analyses.
We also provide a Docker image to use the same runtime environment we used, and a demo to quickly test the methods on real data.

@@

\begin{figure}
\hypertarget{fig:sup:crispr:fig1}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/figure1.png}
\caption{\textbf{EVOS Fluorescence Microscope Image Capture.}
A. HepG2\_lentiV2\_Ctrl with no-viral transduction.
B. HepG2\_lentiV2 with viral transduction.
Both no-viral transduction Control (A) and lentiviral transduction (B) HepG2 cells were stained with LipidSpot™488.
The CRISPR screening process was performed once, but we conducted two selections (high and low fluorescence) with a control of no/before selection. Subsequently, we generated three technical replicates for the RNA-seq libraries under each condition. In order to mitigate false positives resulting from the single-screen process, we overlapped the candidates from multiple pairwise differential analyses and selected the genes that were consistent between selections.}\label{fig:sup:crispr:fig1}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:sup:crispr:fig3}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/figure3.png}
\caption{\textbf{Verification of sgRNA cassette and lentiV2 transgene.}
A. 20nt sgRNA cassette was verified in lentiV2 transduced genomic DNA population, 163 bp PCR product obtained, while WT HepG2 didn't possess the cassette, thus, no PCR product.
B. lentiviral-specific transgene WPRE was verified in lentiV2 transduced genomic DNA population, while no transduced WT didn't have the transgene, therefore, no 173 bp PCR product observed.
For both panels A and B, 100 bp ladder was used in Lane 0.
The CRISPR screening process was performed once, but we conducted two selections (high and low fluorescence) with a control of no/before selection. Subsequently, we generated three technical replicates for the RNA-seq libraries under each condition. In order to mitigate false positives resulting from the single-screen process, we overlapped the candidates from multiple pairwise differential analyses and selected the genes that were consistent between selections.}\label{fig:sup:crispr:fig3}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:sup:crispr:fig4}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/figure4.png}
\caption{\textbf{Illumina library generation.}
A. Construct for generating Illumina libraries.
B. Final Illumina library from HS DNA ---showed a single \textasciitilde285bp peak was generated.
The CRISPR screening process was performed once, but we conducted two selections (high and low fluorescence) with a control of no/before selection. Subsequently, we generated three technical replicates for the RNA-seq libraries under each condition. In order to mitigate false positives resulting from the single-screen process, we overlapped the candidates from multiple pairwise differential analyses and selected the genes that were consistent between selections.}\label{fig:sup:crispr:fig4}
}
\end{figure}

>>>>

For the CRISPR screening, we used FlowJo v10.7 and FACS Jazz software v1.0.
For data analysis, we used Python 3.8 and R 3.6 with several computational packages.
The main Python packages used were: Jupyter Lab (2.2), pandas (1.1), matplotlib (3.3), seaborn (0.11), numpy (1.19), scipy (1.5), scikit-learn (0.23), and umap-learn (0.4).
The main R packages were: Bioconductor (3.10), clusterProfiler (3.14), clustree (0.4), and fgsea (1.17).
We also developed several scripts and notebooks which are published under an open-source license.
We documented all the steps necessary to carry out all the analyses.
We also provide a Docker image to use the same runtime environment we used, and a demo to quickly test the methods on real data.

@@

\begin{figure}
\hypertarget{fig:sup:crispr:fig1}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/figure1.png}
\caption{\textbf{EVOS Fluorescence Microscope Image Capture.}
A. HepG2\_lentiV2\_Ctrl with no-viral transduction.
B. HepG2\_lentiV2 with viral transduction.
Both no-viral transduction Control (A) and lentiviral transduction (B) HepG2 cells were stained with LipidSpot™488.
The CRISPR screening process was performed once, but we conducted two selections (high and low fluorescence) with a control of no/before selection. Subsequently, we generated three technical replicates for the DNA-seq libraries under each condition. In order to mitigate false positives resulting from the single-screen process, we overlapped the candidates from multiple pairwise differential analyses and selected the genes that were consistent between selections.}\label{fig:sup:crispr:fig1}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:sup:crispr:fig3}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/figure3.png}
\caption{\textbf{Verification of sgRNA cassette and lentiV2 transgene.}
A. 20nt sgRNA cassette was verified in lentiV2 transduced genomic DNA population, 163 bp PCR product obtained, while WT HepG2 didn't possess the cassette, thus, no PCR product.
B. lentiviral-specific transgene WPRE was verified in lentiV2 transduced genomic DNA population, while no transduced WT didn't have the transgene, therefore, no 173 bp PCR product observed.
For both panels A and B, 100 bp ladder was used in Lane 0.
The CRISPR screening process was performed once, but we conducted two selections (high and low fluorescence) with a control of no/before selection. Subsequently, we generated three technical replicates for the DNA-seq libraries under each condition. In order to mitigate false positives resulting from the single-screen process, we overlapped the candidates from multiple pairwise differential analyses and selected the genes that were consistent between selections.}\label{fig:sup:crispr:fig3}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:sup:crispr:fig4}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/figure4.png}
\caption{\textbf{Illumina library generation.}
A. Construct for generating Illumina libraries.
B. Final Illumina library from HS DNA ---showed a single \textasciitilde285bp peak was generated.
The CRISPR screening process was performed once, but we conducted two selections (high and low fluorescence) with a control of no/before selection. Subsequently, we generated three technical replicates for the DNA-seq libraries under each condition. In order to mitigate false positives resulting from the single-screen process, we overlapped the candidates from multiple pairwise differential analyses and selected the genes that were consistent between selections.}\label{fig:sup:crispr:fig4}
}
\end{figure}
